Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-10-24 ms/manuscript.Rmd
Update references

---
title: "Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns"
bibliography: "references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968, @Wollenweber2000
---

@@

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/canopylife. Raw and processed data are openly available from the Dryad repository at http://doi.org/ADD_DOI_HERE_WHEN_ASSIGNED [@Nitta2019].

@@

Presence of hairs and glands in gametophytes has very strong phylogenetic signal (\tab \@ref(tab:phylosig-binary)), and these traits are associated with certain taxonomic groups [@Stokey1951; @Nayar1971].
Although hairs have been hypothesized to reduce rates of drying and increase water uptake after desiccation [@Kappen2007], we did not detect a correlation between hair production and epiphytic growth.
Similarly, production of glands does not appear to be correlated with epiphytic growth.
Wax-secreting glands are prevalent in both sporophytes and gametophytes of many notholaenid ferns, a xeric-adapted clade, but their functional significance has not been established [@Johnson2012].
Further tests are needed to determine if such glands serve a functional role in preventing water loss in desert ferns and epiphytes.

>>>>

---
title: "Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns"
bibliography: "references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
nocite: | 
  @Vogel1968
---

@@

Code to replicate all analyses, figures, and this manuscript are available at https://github.com/joelnitta/canopylife. Raw and processed data are openly available from the Dryad repository at http://doi.org/ADD_DOI_HERE_WHEN_ASSIGNED [@Nitta2019a].

@@

Presence of hairs and glands in gametophytes has very strong phylogenetic signal (\tab \@ref(tab:phylosig-binary)), and these traits are associated with certain taxonomic groups [@Stokey1951; @Nayar1971].
Although hairs have been hypothesized to reduce rates of drying and increase water uptake after desiccation [@Kappen2007], and glands may affect rates of osmosis by modifying lipid concentrations [@Crow2011], we did not detect a correlation between hair or gland production and epiphytic growth.
Wax-secreting glands are prevalent in both sporophytes and gametophytes of many notholaenid ferns, a xeric-adapted clade, but their functional significance has not been established [@Johnson2012].
Further tests are needed to determine if such glands serve a functional role in preventing water loss in desert ferns and epiphytes.
